\bf\mftitle

### 2011-03-01 doc/jInfer/runner/runner.tex
propset ignore and package names corrected, nocite corrected
3187368 - Review documentation: cleanup - runner done

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Matej Vitásek \\ \hline
Required tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.IGGenerator \\
 & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator \\
 & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.Simplifier \\ 
 & org.openide.windows.IOProvider \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & Base \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.runner \\
  & cz.cuni.mff.ksi.jinfer.runner.properties \\ \hline
\end{tabular}

@@

\jmodule{Runner} it the module responsible for inference process. The fact that the inference consists of exactly 3 steps as described in TODO link architecture is hard-wired in jInfer via this module.

@@

The only public method in \code{Runner} is, unsurprisingly, \code{run()}. This method will start the first step of the inference process by invoking the selected \jmodule{IGGenerator}'s \code{start()} method, as described in TODO link inference process in architecture. Callback methods \code{finishedIGGenerator()}, \code{finishedSimplifier()} and \code{finishedSchemaGenerator()} are responsible for invoking the following stages of inference, or in the latter case for presenting the resulting schema to the user and terminating the inference process.\\

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Matej Vitásek \\ \hline
Required tokens       & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.IGGenerator} \\
 & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator} \\
 & \code{cz.cuni.mff.ksi.jinfer.base.interfaces.inference.Simplifier} \\ 
 & \code{org.openide.windows.IOProvider} \\ \hline
Provided tokens       & none \\ \hline
Module dependencies   & Base \\ \hline
Public packages       & \code{cz.cuni.mff.ksi.jinfer.runner} \\
  & \code{cz.cuni.mff.ksi.jinfer.runner.properties} \\ \hline
\end{tabular}

@@

\jmodule{Runner} it the module responsible for inference process. The fact that the inference consists of exactly 3 steps as described in \cite{archdoc}, is hard-wired in jInfer via this module.

@@

The only public method in \code{Runner} is, unsurprisingly, \code{run()}. This method will start the first step of the inference process by invoking the selected \jmodule{IGGenerator}'s \code{start()} method, as described in \cite[section 3.5.1]{archdoc}. Callback methods \code{finishedIGGenerator()}, \code{finishedSimplifier()} and \code{finishedSchemaGenerator()} are responsible for invoking the following stages of inference, or in the latter case for presenting the resulting schema to the user and terminating the inference process.\\
